Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-08 draft.tex
add ctn values, remove BR language from defn 2; note Lem 4 not necessary when res:newb holds

\item \textit{Either (a) $\frac{L_s^0}{1-\delta}  > \frac{\omega_s^0}{1-\delta}$ or (b) $0 > \frac{\lambda p_s - \alpha (1-p_s)}{1-\de} > -\mu$: either the secessionists prefer ceding to war or the patron's disutility from war is greater than the per-period cost of offsetting the deterioration in the secessionists' status quo payoffs.}\label{res:new}

@@

The strategies for the government and secessionists in this equilibrium are to play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted below, playing Status Quo is the best response for both inside actors.

@@

\begin{enumerate}
	\item The patron invests $R_p^t = \max\left\{\frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right),0\right\}$ to augment $Q_s^{t-1}$. Player $c$ invests $R_c^t =0$ to augment $L_s^{t-1}$.

If $R_p^t < \frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right)$ player $c$ invests $R_c^t = L_s^{t-1} - \left(Q_s^{t-1} - \mu + R_p^t \right) + \ve$, for $\ve$ small, to augment $L_s^{t-1}$. Cede becomes the unique best response for the secessionists.

@@

If $R_p^t > \frac{\nu}{1-\de} + \left( Q_g^{t-1} - L_g^{t-1}\right)$ to augment $L_g^{t-1}$, player $c$ invests $R_c^t = 0$. Cede becomes the unique best response for the government.

@@

If $R_p^t > \frac{1}{p_s}\left[\frac{\nu p_s - \beta (1-p_s)}{1 -\de} - \mu + Q_s^{t-1} - \left(-\zeta_{s}(1-\de) + W_s^{t-1}p_s + L_s^{t-1}(1-p_s)\right)\right] $ to augment $W_s^{t-1}$, player $c$ will choose $R_c^t=0$. Fight becomes the unique best response for the secessionists.
\end{enumerate}
\end{definition}

@@

One last possibility is ruled out by Lemma 4: that the patron would invest to encourage the secessionists to fight.

@@

If Restriction \ref{res:new}a is violated, as the secessionists' status quo payoffs degrade from period to period, they will fall below $\omega_s^t$ before they fall below $L_s^t$. If no investment is made in $Q_s^{t-1}$, the secessionists will choose the war outcome. Restriction \ref{res:new}b guarantees that the patron will make the investment $R_p^{t'}  = \omega_s^{t-1} -\mu - Q_s^{t-1} \leq \mu$ to prevent the secessionists choosing war since this $R_p^{t'}$ is strictly less than the patron's expected loss from the war outcome. Note that the patron's actual investment will be the maximum of the investment required to prevent the war and ceding outcomes. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 3} \\
Again, in the status quo, we have $U_p^{t,SQ}= -R_p^{SQ}$ and $U_c^{t,SQ}= -R_c^{SQ}$. If the outcome is recognition of the secessionists, per-period payoffs in this absorbing state become $U_p^{t,REC}= \lambda -R_p^{REC}$ and $U_c^{t,REC}= -\nu -R_c^{REC}$ where $SQ$ and $REC$ distinguish investments under the status quo and recognition scenarios respectively.

>>>>

\item \textit{Either (a) $\frac{L_s^0}{1-\delta}  > \frac{\omega_s^0}{1-\delta}$ or (b) $0 > -\mu > \frac{\lambda p_s - \alpha (1-p_s)}{1-\de}$: either the secessionists prefer ceding to war or the patron's disutility from war is greater than the per-period cost of offsetting the deterioration in the secessionists' status quo payoffs.}\label{res:new}

@@

The strategies for the government and secessionists in this equilibrium are to play their best responses given the continuation values induced by the investments of the outside actors. The continuation value from choosing war is the expected future stream of payoffs from the two possible absorbing states net of the cost of war $\left(-\zeta_i +\frac{W_i^t(p_i)+ L_i^t(1-p_i)}{1-\delta}\right)$. Similarly, the continuation value from ceding is $\frac{L_i^t}{1-\de}$ while that for the status quo is $\sum_{s=t}^\infty \de^{t-s} Q_i^t$. Unless otherwise noted below, playing Status Quo is the dynamic best response for both inside actors.

@@

\begin{enumerate}
	\item The patron invests $R_p^t = \max\left\{\frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right),\frac{\omega_s^{t-1}}{1-\de} +\mu - \frac{Q_s^{t-1}}{1-\de},0\right\}$ to augment $Q_s^{t-1}$. Player $c$ invests $R_c^t =0$ to augment $L_s^{t-1}$.

If $\frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right) > 0$ and $R_p^t < \frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right)$, player $c$ invests $R_c^t = L_s^{t-1} - \left(Q_s^{t-1} - \mu + R_p^t \right) + \ve$, for $\ve$ small, to augment $L_s^{t-1}$ so that the secessionists play Cede.

@@

If the patron invests $R_p^t > \frac{\nu}{1-\de} + \left( Q_g^{t-1} - L_g^{t-1}\right)$ to augment $L_g^{t-1}$, player $c$ is deterred from investing in $Q_g^{t-1}$ ($R_c^t = 0$) so that the government plays Cede.

@@

If the patron invests $R_p^t > \frac{1}{p_s}\left[\frac{\nu p_s - \beta (1-p_s)}{1 -\de} - \mu + Q_s^{t-1} - \left(-\zeta_{s}(1-\de) + W_s^{t-1}p_s + L_s^{t-1}(1-p_s)\right)\right] $ to augment $W_s^{t-1}$, player $c$ is deterred from investing in $Q_s^{t-1}$ ($R_c^t=0$) so that the secessionists play Fight.
\end{enumerate}
\end{definition}

@@

One last possibility is ruled out by Lemma 4: that the patron would invest to encourage the secessionists to fight. Note that the patron has no incentive to make this investment if Restriction \ref{res:new}b holds.

@@

If Restriction \ref{res:new}a is violated, as the secessionists' status quo payoffs degrade from period to period, they will fall below $\omega_s^t$ before they fall below $L_s^t$. If no investment is made in $Q_s^{t-1}$, the secessionists will choose the war outcome. Restriction \ref{res:new}b guarantees that the patron will make the investment $R_p^{t'}  = \frac{\omega_s^{t-1}}{1-\de} +\mu - \frac{Q_s^{t-1}}{1-\de} \leq \mu$ to prevent the secessionists choosing war since this $R_p^{t'}$ is strictly less than the patron's expected loss from the war outcome. Note that the patron's actual investment will be the maximum of the investment required to prevent the war and ceding outcomes. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 3} \\
Again, in the status quo, we have $U_p^{t,SQ}= -R_p^{SQ}$ and $U_c^{t,SQ}= -R_c^{SQ}$. If the outcome is recognition of the secessionists, per-period payoffs in this absorbing state become $U_p^{t,REC}= \lambda -R_p^{REC}$ and $U_c^{t,REC}= -\nu -R_c^{REC}$ where $SQ$ and $REC$ distinguish investments under the status quo and recognition scenarios respectively.
